---
title: "graphicMiscue"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  md_document:
    toc: true      
---

```{r, echo=FALSE}
desc <- suppressWarnings(readLines("DESCRIPTION"))
regex <- "(^Version:\\s+)(\\d+\\.\\d+\\.\\d+)"
loc <- grep(regex, desc)
ver <- gsub(regex, "\\2", desc[loc])
#verbadge <- sprintf('<a href="https://img.shields.io/badge/Version-%s-orange.svg"><img src="https://img.shields.io/badge/Version-%s-orange.svg" alt="Version"/></a></p>', ver, ver)
verbadge <- ''
````

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
knit_hooks$set(htmlcap = function(before, options, envir) {
  if(!before) {
    paste('<p class="caption"><b><em>',options$htmlcap,"</em></b></p>",sep="")
    }
    })
knitr::opts_knit$set(self.contained = TRUE, cache = FALSE, fig.align = 'center')
knitr::opts_chunk$set(fig.path = "tools/figure/")
options(scipen=999)
```


[![Build Status](https://travis-ci.org/trinker/graphicMiscue.svg?branch=master)](https://travis-ci.org/trinker/graphicMiscue)
[![Coverage Status](https://coveralls.io/repos/trinker/graphicMiscue/badge.svg?branch=master)](https://coveralls.io/r/trinker/graphicMiscue?branch=master)
`r verbadge`

**graphicMiscue** is a minimal package for analyzing miscues graphically.  Not for general public consumption.

# Installation

To download the development version of **graphicMiscue**:

Download the [zip ball](https://github.com/trinker/graphicMiscue/zipball/master) or [tar ball](https://github.com/trinker/graphicMiscue/tarball/master), decompress and run `R CMD INSTALL` on it, or use the **pacman** package to install the development version:

```r
if (!require("pacman")) install.packages("pacman")
pacman::p_load_current_gh("trinker/graphicMiscue")
```

# Contact

You are welcome to:    
- submit suggestions and bug-reports at: <https://github.com/trinker/graphicMiscue/issues>    
- send a pull request on: <https://github.com/trinker/graphicMiscue>    
- compose a friendly e-mail to: <tyler.rinker@gmail.com>    
